\PaperTitle

### 2024-05-05 Final_Report/paper.tex
Fixed table placeent and some figure references

You'll notice in the heatmaps in figures \ref{knn_heatmap}, \ref{rf_heatmap}, and \ref{nn_heatmap} that chatGPT is classified 100\% accurately by RF and NN, and is very close with KNN.

@@

Since Protocol wasn't deterministic at all for LinkedIn and Blackboard, the explanatory power that our model had must have come from Time and/or Length. In figure \ref{time_scatter}, see that Blackboard has significantly lower time values that LinkedIn. 
This is likely where most of the explanatory power came from since length has a similar distribution between all websites, as per \ref{length_scatter}.

>>>>

You'll notice in the heatmaps in figures \ref{fig:knn_heatmap}, \ref{fig:rf_heatmap}, and \ref{fig:nn_heatmap} that chatGPT is classified 100\% accurately by RF and NN, and is very close with KNN.

@@

Since Protocol wasn't deterministic at all for LinkedIn and Blackboard, the explanatory power that our model had must have come from Time and/or Length. In figure \ref{fig:time_scatter}, see that Blackboard has significantly lower time values that LinkedIn. 
This is likely where most of the explanatory power came from since length has a similar distribution between all websites, as per figure \ref{fig:length_scatter}.
